Counting the Cockroaches in the Walls or I Know Why the Caged Bird Tweets: Assessing the Severity of Service Failures Through Social Chatter

### 2019-04-19 Paper/README.Rmd
Cleaning up the old latex code
Added MIT and Creative Common licenses

@@

To illustrate, suppose a firm uses feedback reported on Twitter to assess service failure severity in order to simply determine their competitive position in the marketplace (e.g., the firm with the fewest complaints is the market leader). To do this, they simply count the number of negative tweets (i.e., complaints) for each firm for a given type of service failure. After accounting for differences in firm size, how accurately do these counts measure the true size of the population affected by the service failure (i.e., the reach of the service failure)? The counts could \emph{underestimate} the population size because not everyone that experiences a failure tweets about it. However, users could tweet more than once, experience multiple failures, tweet a complaint without experiencing the failure, or be influenced by network effects -- which would all lead to observed counts that \emph{overestimate} the true population size. We propose a model that explicitly disentangles the propensity to complain from the propensity to exaggerate complaints.

>>>>

License: This work is licensed under a [Creative Commons Attribution-ShareAlike 4.0 International License](https://creativecommons.org/licenses/by-sa/4.0/).

@@

To illustrate, suppose a firm uses feedback reported on Twitter to assess service failure severity in order to simply determine their competitive position in the marketplace (e.g., the firm with the fewest complaints is the market leader). To do this, they simply count the number of negative tweets (i.e., complaints) for each firm for a given type of service failure. After accounting for differences in firm size, how accurately do these counts measure the true size of the population affected by the service failure (i.e., the reach of the service failure)? The counts could underestimate the population size because not everyone that experiences a failure tweets about it. However, users could tweet more than once, experience multiple failures, tweet a complaint without experiencing the failure, or be influenced by network effects -- which would all lead to observed counts that \emph{overestimate} the true population size. We propose a model that explicitly disentangles the propensity to complain from the propensity to exaggerate complaints.
